\documentclass[letterpaper]{article}

\usepackage[margin=0.42in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, itemsep=0pt, topsep=1pt, parsep=0pt, partopsep=0pt}
\titleformat{\section}{\normalsize\bfseries}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{2pt}{1pt}

\newcommand{\roleline}[3]{
  \textbf{#1} \hfill #2 \\
  \textit{#3} \\
}
\newcommand{\projectheader}[2]{
  \textbf{#1} \\
  \textit{#2} \\
}

\begin{document}
\footnotesize

\begin{center}
    {\LARGE \textbf{Fares Mohamed}}\\[4pt]
    Alexandria, Egypt \,|\, \href{mailto:faresmohamed260@gmail.com}{faresmohamed260@gmail.com} \\
    GitHub: \href{https://github.com/faresmohamed260}{github.com/faresmohamed260} \,|\, LinkedIn: \href{https://www.linkedin.com/in/fares-mohamed-b83454194/}{linkedin.com/in/fares-mohamed-b83454194}\\[2pt]
    \textbf{AI Engineer} \,|\, Agentic AI Systems, LLM Orchestration, Tool-Integrated Workflows
\end{center}

\section*{Summary}
2026 Computer Science graduate focused on agentic AI systems, retrieval-grounded LLM workflows, and production-minded AI tooling across Python, FastAPI, React, Streamlit, and automation platforms.

\section*{Experience}
\roleline{Armstrong}{Apr 2025 -- Sep 2025}{AI \& Automation Engineer, Alexandria, Egypt}
\begin{itemize}
    \item Built AI-driven automation pipelines for the Digital Egypt Cubs Initiative (DECI), a national educational initiative under Egypt's Ministry of Communications and Information Technology (MCIT).
    \item Designed scalable workflows using n8n, LLM systems, custom GPTs, and open-source AI models to automate educational content generation.
    \item Reduced manual workload through automation-first pipeline design, AI-assisted content production, and visual asset orchestration.
\end{itemize}

\roleline{Armstrong}{Jun 2025 -- Sep 2025}{Technical Content Creator, Alexandria, Egypt}
\begin{itemize}
    \item Created technical educational content focused on robotics, AI, Arduino, circuits, and programming.
    \item Developed structured STEM learning materials including presentations, instructional guides, and educational videos.
    \item Simplified complex engineering concepts into accessible learning experiences for students and educators.
\end{itemize}

\roleline{Kayfa}{Aug 2025 -- Dec 2025}{AI Subject Matter Expert, Alexandria, Egypt}
\begin{itemize}
    \item Developed structured educational content covering machine learning, neural networks, convolutional neural networks (CNNs), and unsupervised learning concepts.
    \item Created technical lessons, assignments, and implementation-focused notebooks explaining clustering, anomaly detection, ANN architectures, activation functions, and deep learning fundamentals.
    \item Designed practical AI learning materials combining theoretical concepts with hands-on workflows using Python and machine learning tools.
\end{itemize}

\roleline{Engineering for Kids-Egypt}{Jun 2025 -- Aug 2025}{AI \& Robotics Instructor, Alexandria, Egypt}
\begin{itemize}
    \item Taught robotics, AI, Arduino, circuits, Python, and C++ to students aged 11--16.
    \item Guided hands-on engineering and programming projects focused on problem-solving and creativity.
    \item Delivered interactive STEM learning experiences combining software and hardware concepts.
\end{itemize}

\section*{Projects}
\projectheader{SAGA: Database-Native Agentic AI Workspace}{Python, FastAPI, React, SQLite, Streamlit, RAG}
\href{https://github.com/faresmohamed260/saga}{github.com/faresmohamed260/saga}\\
\begin{itemize}
    \item Built a narrative intelligence workspace for books that ingests EPUB and PDF sources, extracts structured canon, and supports grounded analysis, retrieval, and downstream story-generation workflows.
    \item Designed a database-native agent pipeline for events, entities, character profiles, timelines, and world state so outputs stay inspectable, reusable, and resumable across runs.
    \item Implemented schema-constrained extraction, strict JSON outputs, retrieval-grounded reasoning, and a React + FastAPI dashboard for workflow control.
\end{itemize}

\projectheader{DUM-E: ESP32 Robotic Arm Platform}{Python, ESP32, Streamlit, Robotics}
\href{https://github.com/faresmohamed260/DUM-E}{github.com/faresmohamed260/DUM-E}\\
\begin{itemize}
    \item Built a robotics control platform for a programmable ESP32-based arm that supports calibration, manual control, and repeatable task execution through a software operator interface.
    \item Combined embedded control, a Streamlit dashboard, and FK/IK-assisted motion planning for repeatable demonstrations.
\end{itemize}

\section*{Education}
\textbf{Alexandria University, Faculty of Computer and Data Science} \hfill 2022 -- 2026\\
B.Sc. in Computer Science (Intelligent Systems), Alexandria, Egypt\\

\section*{Leadership}
\textbf{ElCoder} \\
Head of AI Committee, Alexandria, Egypt\\
Led student workshops and technical sessions on AI and machine learning fundamentals.\\

\section*{Skills}
\textbf{Languages \& Tools:} Python, C++, FastAPI, React, Streamlit, Docker, SQLite, n8n, Arduino, ESP32\\
\textbf{Agentic AI:} LLM orchestration, multi-stage workflows, prompt engineering, structured outputs, tool-calling patterns, retrieval-augmented generation (RAG)\\
\textbf{Applied AI:} NLP, computer vision, multimodal systems, workflow automation, robotics-aware interfaces\\
\textbf{Languages:} Arabic, English

\section*{Certifications}
Machine Learning Specialization \,|\, Deep Learning Specialization \,|\, Google Cloud Big Data and Machine Learning Fundamentals

\end{document}
